Precise spiking motifs in neurobiological and neuromorphic data

### 2022-12-19 manuscript.tex
in sync: \acknowledgments

Indeed, we had made that choice to study precise temporal motifs. In the new manuscript, we mention these alternative options briefly even if we keep the focus on deterministic spiking motifs for this review.

@@

\acknowledgments{We would like to thank Jean-Nicolas Jérémie, George Abitbol and Hugo Ladret for useful discussions while writing this review.}

>>>>

Indeed, we had made that choice to

@@

\acknowledgments{We would like to thank George Abitbol and Hugo Ladret for useful feedbacks while writing this review. Many thanks to Simon Thorpe for the useful discussions and references on the latency of the visual system in human and non-human primates.}
